Impact of IPTp Regimen on Pregnancy Outcomes in a Malaria-Endemic Setting

### 2025-04-30 products/manuscript/Manuscript.qmd
update1

**Figure 1: Distribution of Total Malaria Episodes by IPTp Treatment Arm**
```{r,echo=FALSE, message=FALSE, warning=FALSE}}
knitr::include_graphics("Images/Figure1.DistribTotal Malaria.png")
```

@@

**Table 2: Outcome Measures and Malaria Exposure Variables Stratified by IPTp Regimen**
```{r}
knitr::include_graphics("Images/Table2.Outcome Measures Malaria .png")
```

@@

**Figure 2: Differential Impact of IPTp Treatment on the Relationship Between Malaria Episodes and Adverse Birth Outcomes**
```{r}
knitr::include_graphics("Images/Figure2.Differential Impact of IPTp.png")
```

@@

**Table 3: Interaction Between Malaria Exposure and IPTp Treatment Arm in Predicting Adverse Birth Outcomes**

```{r,echo=FALSE, message=FALSE, warning=FALSE}
knitr::include_graphics("Images/Table4Interaction.png")
```

@@

**Figure 4: Predicted Probability of Adverse Outcome by Gravidity (Age < 25)**
```{r, echo=FALSE, message=FALSE, warning=FALSE}
knitr::include_graphics("Images/Figure 3. Predicted Probability.png")
```

@@

**Table 5:  Discriminative Performance (AUC) of Machine Learning Models Predicting Adverse Birth Outcomes Under Different IPTp Regimens**
```{r, echo=FALSE, message=FALSE, warning=FALSE}
knitr::include_graphics("Images/Table6.Discriminative Performance (AUC) of ML Models.png")
```

@@

**Figure 5 : Comparative Discriminative Performance of ML Models for Predicting Adverse Birth Outcomes**
```{r, echo=FALSE, message=FALSE, warning=FALSE}
knitr::include_graphics("Images/Figure 4.Comparative Discriminative Performance of ML .png")
```

>>>>

**Figure 1: Distribution of Total Malaria Episodes by IPTp Treatment Arm**
```{r,echo=FALSE, message=FALSE, warning=FALSE}
knitr::include_graphics("Images/Figure1.DistribTotalMalaria.png")
```

@@

**Table 2: Outcome Measures and Malaria Exposure Variables Stratified by IPTp Regimen**

```{r echo=FALSE, message=FALSE, warning=FALSE}
knitr::include_graphics("Images/Table2.OutcomeMeasuresandMalariaExposure.png")
```

@@

**Figure 2: Differential Impact of IPTp Treatment on the Relationship Between Malaria Episodes and Adverse Birth Outcomes**
```{r echo=FALSE, message=FALSE, warning=FALSE}
knitr::include_graphics("Images/Figure2.DifferentialImpactofIPTp.png")
```

@@

**Table 3: Interaction Between Malaria Exposure and IPTp Treatment Arm in Predicting Adverse Birth Outcomes**
```{r echo=FALSE, message=FALSE, warning=FALSE}
knitr::include_graphics("Images/Table3Interaction.png")
```

@@

**Figure 4: Predicted Probability of Adverse Outcome by Gravidity (Age < 25)**
```{r echo=FALSE, message=FALSE, warning=FALSE}
knitr::include_graphics("Images/Figure3.PredictedProbability.png")
```

@@

**Table 5:  Discriminative Performance (AUC) of Machine Learning Models Predicting Adverse Birth Outcomes Under Different IPTp Regimens**
```{r echo=FALSE, message=FALSE, warning=FALSE}
knitr::include_graphics("Images/Table6.DiscriminativePerformance(AUC)ofMLModels.png")
```

@@

**Figure 5 : Comparative Discriminative Performance of ML Models for Predicting Adverse Birth Outcomes**
```{r echo=FALSE, message=FALSE, warning=FALSE}
knitr::include_graphics("Images/Figure5Calibration.png")
```
